A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-10-19 doc/large_strain.tex
typo

where in the last step $\tilde{a}(\gz N_i,\gz N_j)(\gz \xi_q)$ is a representation for the evaluation of the bilinear form in one quadrature point on isoparametric element $\gz \xi_q$ and $J^K$ is the Jacobian of the mapping from the isoparametric to the element $K$.

>>>>

where in the last step $\tilde{a}(\gz N_i,\gz N_j)(\gz \xi_q)$ is a representation for the evaluation of the bilinear form in one quadrature point on isoparametric element $\gz \xi_q$ and $J^K$ is the Jacobian of the mapping from the isoparametric element to the element $K$.
